Single-cell virus sequencing of influenza variants that trigger innate immunity

### 2018-09-12 paper/paper.tex
Added references to pacbio and qPCR method section, as well as including additional cycle data. Have also added a supplementary text file describing all primers used for PacBio enrichment

@@

\subsection{Enrichment and preparation of viral cDNA for PacBio sequencing}
All PCR amplifications were performed using Kapa HiFi Hotstart Readymix.
In order to enrich full-length cDNA derived from influenza transcripts, 1ng of full-length 10x-barcoded cDNA was used as template in a multiplex PCR reaction using eight segment-specific 5' primers and a shared, 10x-specific 3' primer \abrcomment{supplemental text}.
To reduce strand-exchange and generate more even amplification across segments, this reaction was performed in an emulsion PCR using the Micellula DNA Emulsion Kit from Roboklon, supplementing our PCR reaction with additional BSA to a final concentration of 0.1mg/ml.
Emulsion PCR involves encapsidating DNA template molecules in a reverse-phase emulsion, with each template positive droplet serving as a microreactor.
This process physically separates disparate template molecules, preventing strand exchange, and, moreover, allowing each molecule to be amplified to exhaustion of its droplet's reagents without competing with the broader pool of PCR-amenable molecules.
To reach this level of reagent exhaustion, for all emulsion PCRs described here, 30 rounds of PCR was performed in order to saturate emulsion materials---unlike open PCR reactions, the physical occlusion of amplified material reduces artifacts at high cycle numbers.

>>>>

\figdata{textfile providing all primer sequences used to amplify and enrich influenza transcripts for PacBio sequencing. \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/tree/master/paper/figures/WorkflowSchematic/PacBio_primer_list.txt} 
}
\label{figdata:primer_sequences}

@@

\subsection{Enrichment and preparation of viral cDNA for PacBio sequencing}
Sequences of all primers described below are described in  \FIGDATA[experiment]{primer_sequences}.
All PCR amplifications were performed using Kapa HiFi Hotstart Readymix in a 100$\mu$l volume.
In order to enrich full-length cDNA derived from influenza transcripts, 1ng of full-length 10x-barcoded cDNA was used as template in a multiplex PCR reaction using eight segment-specific 5' primers and a shared, 10x-specific 3' primer.
To reduce strand-exchange and generate more even amplification across segments, this reaction was performed in an emulsion PCR using the Micellula DNA Emulsion Kit from Roboklon, supplementing our PCR reaction with additional BSA to a final concentration of 0.1mg/ml and an aqueous phase of 100$\mu$l .
Emulsion PCR involves encapsidating DNA template molecules in a reverse-phase emulsion, with each template positive droplet serving as a microreactor.
This process physically separates disparate template molecules, preventing strand exchange, and, moreover, allowing each molecule to be amplified to exhaustion of its droplet's reagents without competing with the broader pool of PCR-amenable molecules~\citep{Boers:2015emulsion}.
To reach this level of reagent exhaustion, for all emulsion PCRs described here, 30 rounds of PCR was performed in order to saturate emulsion materials---unlike open PCR reactions, the physical occlusion of amplified material reduces artifacts at high cycle numbers.
